Modelling the City of Melbourne Pedestrian Data

### 2017-10-01 presentation/final.Rmd
added final/future steps for the prject - may need to either add more points or elaborate on points already there
update - more detailed future steps

- general code which will run the algorithm
- inputs required: 
  * data in wide format
  * threshold value for missing values proportion (_default:_ `threshold = 0.1`)
  * max length of repeated values (_default:_ `maxlength = 17`)
- use R and RStudio with packages:
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data
---
## Imputation Model Evaluation
### In-sample Fit

@@

>>>>

- general code which will run the algorithm
- inputs required: 
  * data in wide format
  * threshold value for missing values proportion (_default:_ `threshold = 0.1`)
  * max length of repeated values (_default:_ `maxlength = 17`)
- use R and RStudio with packages:
  * `dplyr`, `lubridate` and `tidyr` for data manipulation
  * `foreach` and `doSNOW` for parallel computing
  * `rwalkr` for accessing latest data
---
class: center
## Imputation Model Evaluation
### In-sample fit

@@

### Objective: On the fly predictions of pedestrian traffic
- requires efficient data storage

---
# Future steps for final paper
- develop Shiny app wih RStudio to provide on the fly predictions
  * make the predictive models more accessible
  * provide visualisations to present the predictions

```{r, cache = TRUE, fig.retina = 4, echo = FALSE, message = FALSE, fig.align= 'center', fig.width=5, fig.height=4, warning=F}
mar13_16_8am <- ped_data[ped_data$Date == "2016-03-13", ] %>%
                filter(Time == 8)

loc$Sensor <- loc$ids

mar13_16_8am %>% left_join(loc) -> mar13_16_8am

bourkest_loc <- loc[loc$ids == "Flinders St Station Underpass",]

  melb_dark <- get_map(location=c(bourkest_loc$lons, bourkest_loc$lats),
                                zoom=16, maptype = "toner-lite")

ggmap(melb_dark) + geom_point(aes(x = lons, y = lats, alpha = Count),
                              colour = magma(8)[6],
                      data = mar13_16_8am, shape = 15, size = 16) +
              scale_alpha_continuous(range = c(.1, .6)) +
              theme_minimal() +
                theme(plot.title = element_text(hjust = 0.5),
                    plot.caption = element_text(hjust = 0.5),
                    axis.text.x = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks = element_blank(),
                    legend.position = "right") +
                xlab(NULL) + ylab(NULL) + ggtitle("Pedestrian Traffic around Flinders St \n at 13 Mar 2016, 8AM")

- explore predictors outside of counts data
